\documentclass[a4paper,11pt]{article}
\pagenumbering{arabic}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{xparse}

\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{blue}{#1}}%
}

\lstset{language=C,keywordstyle={\bfseries \color{blue}}}

\begin{document}

\title{Ratus Unilicense 1.0}
\author{Robin Bron}
\date{\today}
\maketitle

\vfill

\input{cc40.tex}
\newpage
\tableofcontents
\newpage

\section{Introduction}
  This document specifies the Ratus Unilicense 1.0 license, targeted at
  providing a restrictive code license for both open source and closed source
  projects while still allowing unrestricted use of the licensed subject.

\subsection{Summary}
  \begin{itemize}
    \item Must
    \begin{itemize}
      \item Include License
    \end{itemize}
    \item Can
    \begin{itemize}
      \item Change license
      \item Sublicense
      \item Private use
      \item Commercial use
      \item Include Original
    \end{itemize}
    \item Limited
    \begin{itemize}
      \item Distribute
      \item Modify
    \end{itemize}
    \item Can't
    \begin{itemize}
      \item Hold Liable
    \end{itemize}
  \end{itemize}

\subsection{Conventions}
\input{rfc2119.tex}

\newpage
\section{The License}

\subsection{Inside a file}
  Ratus Unilicense 1.0 MAY be applied to a single file or document using the
  following text near the start of the file or document, replacing \{name\} by
  the name of the entity holding the rights (most likely your or your company's
  name).

  \begin{quote}
    Copyright (C) \{name\} - All Rights Reserved\newline
    Ratus Unilicense 1.0

    % Disallow spreading like wildfire
    Unauthorized copying, modifying or distribution of this file or document,
    it's derivatives and associated documentation files and/or documents, via
    any medium, is strictly prohibited without the express permission of the
    copyright holder.

    % Apply all rules from the full version
    All but section 1 of Ratus Unilicense 1.0 apply to this file or
    document (the "Software"), as found following the url:
    https://trackthis.nl/license/ratus-unilicense-1.0
  \end{quote}

\newpage
\subsection{Full Version}
  Ratus Unilicense 1.0 SHOULD be applied to a collection of files or documents
  using a single \codeword{LICENSE} file or document in the folder or container
  which holds the files or documents licensed by it.

  To apply Ratus Unilicense 1.0 to the contents of a folder or container, the
  contents of the \codeword{LICENSE} file or document MUST be as follows,
  replacing \{name\} by the name of the entity holding the rights (most likely
  your or your company's name).

  \begin{quote}
    Copyright (C) \{name\} - All Rights Reserved\newline
    Ratus Unilicense 1.0

    % Disallow spreading like wildfire
    1. Copyright\newline
    Unauthorized copying, modifying or distribution of the files and/or
    documents contained in the folder or container holding this license,
    their derivatives and associated files and/or documents (the "Software"),
    via any medium, is strictly prohibited without the express permission of
    the copyright holder.

    % Allow compile & run
    2. Compilation and execution\newline
    Obtained copies of the Software may be compiled and/or executed without
    modification without limitations and warranties.

    % Allow full relicensing by copyright holder
    3. Changing license\newline
    The Software may be distributed under a different license only by the
    copyright holder at which point only the newer license applies to all
    copies of the Software obtained using that license.

    % Allow example code to be copied
    4. Sublicense\newline
    A different license may apply to any, whole or partial, file, document,
    folder or container covered by this license.

    % Waive warranties
    5. Liability\newline
    THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
    IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF FITNESS FOR A
    PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL AUTHORS OR
    COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
    WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF
    OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
    SOFTWARE.

  \end{quote}


%\subsection{Full Version}

\end{document}
